Hydra battles in Coq

### 2020-09-09 latex/chapter-ordinals.tex
minor corrections

@@

@@

@@

\index{Coq!Techniques!Unicity of equality proofs}

@@

\begin{Coqsrc}
Class  ON_Iso 
       `(OA : @ON A ltA compareA)
       `(OB : @ON B ltB  compareB)
       (f : A -> B)
       (g : B -> A):=
  {
  iso_compare: forall x y : A, 
      compareB (f x) (f y) = compareA x y;
  iso_inv1 : forall a, g (f a)= a;
  iso_inv2 : forall b, f (g b) = b}.
\end{Coqsrc}

@@

\index{Projects}
\begin{project}
Add to the class \texttt{ON} the requirement that for any $\alpha$ it is decidable whether $\alpha$ is $0$, a successor pr a mimit ordinal.
\end{project}

@@

\index{Projects}
\begin{project}
Let $N_A$ be a notation system for ordinals strictly less than $\alpha$, 
with the strict order $(A,<_A)$. Please build the notation system
\texttt{ON\_Expl $N_A$}, on the type of multisets of elements of $A$
(or, if preferred, the type of non-increasing finite sequences on $A$,
provided with the lexicographic ordering on lists).

>>>>

\index{Coq!Type classes}
\label{types:ON}

@@

\index{Coq!Type classes}
\label{types:SubON}

@@

\index{Coq!Type classes}
\label{types:ON-for}

@@

\index{Coq!Techniques!Unicity of equality proofs}
\label{sect:eq-proof-unicity}

@@

\index{Coq!Type classes}
\label{types:ON-iso} 
\begin{Coqsrc}
Class  ON_Iso 
       `(OA : @ON A ltA compareA)
       `(OB : @ON B ltB  compareB)
       (f : A -> B)
       (g : B -> A):=
  {
  iso_compare: forall x y : A, 
      compareB (f x) (f y) = compareA x y;
  iso_inv1 : forall a, g (f a)= a;
  iso_inv2 : forall b, f (g b) = b}.
\end{Coqsrc}

@@

\index{Projects}
\begin{project}
\label{project:succ-limit-dec}
Add to the class \texttt{ON} the requirement that for any $\alpha$ it is decidable whether $\alpha$ is $0$, a successor or a limit ordinal.
\end{project}

\index{Projects}
\begin{project}
\label{project:on-setoid}
Reconsider the  class \texttt{ON}, with an equivalence instead of Leibniz equality.
\end{project}

@@

\begin{project}
The directory \texttt{src/OmegaOmega} contains an ad-hoc formalization of $\omega^\omega$, contributed by Pascal Manoury. Every ordinal $\alpha$ is represented by a list $l$ whose elements are the coefficients of $\omega$ in  the Cantor normal form of $\alpha$ (in reverse order). For instance, the ordinal 
$\omega^{8}\times 5 + \omega^{6}\times 8 + \omega^2\times 10 + \omega + 7$ is represented by the list \texttt{[5;0;8;0;0.0;10,1,7]}.

 Develop this representation and compare it with the other ordinal notations.

\begin{project}
Let $N_A$ be a notation system for ordinals strictly less than $\alpha$, 
with the strict order $(A,<_A)$. Please build the notation system
\texttt{ON\_Expl $N_A$}, on the type of multisets of elements of $A$
(or, if preferred, the type of non-increasing finite sequences on $A$,
provided with the lexicographic ordering on lists).
